Distributional Regression Forests for Probabilistic Modeling and Forecasting

### 2020-04-26 pkg/disttree/inst/Psychoco2018/slides.Rnw
slides for PhD thesis defense
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3011 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 2ac42af760b377bd2d56a4a05978e1eca5f1f0e9

%\SweaveOpts{eval=FALSE}
<<sim_1dataset, echo=FALSE, results=hide>>=
set.seed(723)
fun <- function(x){cbind(10*exp(-((4*x[,1]-2)^4)), 0.5 + 2*abs(x[,1]))}
learndata <- dgp(300, family = dist_list_normal, round.sp = 4, fun = fun)
control <-  ctree_control(teststat = "quad", testtype = "Bonferroni", mincriterion = 0.7, minbucket = 20L)
dt <- disttree(y~x1, data=learndata, family=dist_list_normal, type.tree = "ctree", control = control)

if(file.exists("sim_forest.rda")){
  load("sim_forest.rda")
} else {
  control <-  ctree_control(teststat = "quad", testtype = "Univ", mincriterion = 0, minbucket = 7L)
  df <- distforest(y~x1, data=learndata, family=dist_list_normal, ntree = 500L, type.tree = "ctree", control = control)
  df$info <- df$fitted <- df$weights <- df$nodes <- df$data <- df$terms <- df$loglik <- df$trafo <- NULL
  save(df, file = "sim_forest.rda")
}

@@

>>>>

%\SweaveOpts{eval=FALSE}
<<sim_1dataset, echo=FALSE, results=hide>>=
set.seed(723)
fun <- function(x){cbind(10*exp(-((4*x[,1]-2)^4)), 0.5 + 2*abs(x[,1]))}
learndata <- dgp(300, family = dist_list_normal, round.sp = 4, fun = fun)
control <-  disttree_control(type.tree = "ctree", teststat = "quad", testtype = "Bonferroni", mincriterion = 0.7, minbucket = 20L)
dt <- disttree(y~x1, data=learndata, family=dist_list_normal, control = control)

if(file.exists("sim_forest.rda")){
  load("sim_forest.rda")
} else {
  control <-  disttree_control(teststat = "quad", testtype = "Univ", mincriterion = 0, minbucket = 7L,type.tree = "ctree")
  df <- distforest(y~x1, data=learndata, family=dist_list_normal, ntree = 500L, control = control)
  df$info <- df$fitted <- df$weights <- df$nodes <- df$data <- df$terms <- df$loglik <- df$trafo <- NULL
  save(df, file = "sim_forest.rda")
}

@@

\textbf{Alternative:} When no obvious classic distribution assumption is available.
